Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-08-28 main.Rmd
Working on Section 3

 The methods are implemented in the open source R package `gravitas`, providing functions for creating granularities and exploring the associated time series which are consistent with a tidy workflow (@Grolemund2018-po), and the probability distributions can be examined using the range of graphics available in `ggplot2` [@Wickham2009pk].
bibliography: [bibliography.bib]
preamble: >
  \usepackage{mathtools,amssymb,booktabs,amsthm}
  \def\mod{~\text{mod}~}
  \newtheorem{definition}{Definition}
  \newtheorem*{example}{Example}
  \usepackage{mathptmx}
  \usepackage{caption}
  \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
  \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
  \captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
output:
  bookdown::pdf_book:
    base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
    keep_tex: yes
---

@@

Cyclic granularities represent cyclical repetitions in time. They can be thought of as additional categorizations of time that are not linear. Cyclic granularities can be constructed by operating on two linear granularities. Cycles can be either _regular_, called **circular**, or _irregular_, **quasi-circular** when these two linear granularities relate periodically.

@@

\begin{definition}\label{def:circular}
A \textbf{circular granularity} $C_{B, G}$ relates a linear granularity $G$ to the bottom granularity B, if
\begin{equation} \label{eq:circular-gran}
\begin{split}
C_{B, G}(z) & = z\mod P(B, G) \quad \forall z \in \mathbb{Z}_{\geq 0} \\
\end{split}
\end{equation}
where
z denotes the index set,
B denotes a full-integer labelled bottom granularity which groups periodically into linear granularity $G$ with regular mapping, and $P \equiv P(B, G)$ is the number of granules of $B$ in each granule of $G$, also called the period of the grouping $(B, G)$.
\end{definition}

For example, \autoref{fig:circular-dow} illustrates the linear and the corresponding cyclical granularities. Cyclical granularities can be considered to be cutting the linear granularity into pieces, and stacking them to match the cycles (as shown in b). $B, G, H$ (day, week, fortnight, respectively) are linear granularities. The circular granularity $C_{B , G}$ (day-of-week)is constructed from $B$ and $G$. The circular granularity $C_{B, H}$ (day-of-fortnight) is constructed from $B$ and $H$. These overlapping cyclical granularities share elements from the linear granularity. Each of $C_{B , G}$ and $C_{B , H}$ consist of repeated patterns $\{0, 1, \dots, 6\}$ and $\{0, 1, \dots, 13\}$ with $P=7$ and $P=14$ respectively. Each circular granularity can use descriptive label mappings. Suppose ${L}$ is a label mapping that defines an unique label for each index $\ell \in \{ 0,1,\dots, (P-1)\}$, then the label mapping $L$ for $C_{B, G}$ can be defined (for example) as
\begin{align*}
  L: \{0,1, \dots, 6\} & \longmapsto\ \{\text{Sun}, \text{Mon}, \dots, \text{Sat}\}\\
\text{or}\qquad
  L: \{0,1, \dots, 6\} & \longmapsto\ \{\text{Sunday}, \text{Monday}, \dots, \text{Saturday}\}.
\end{align*}

@@

(ref:circular-dow) Illustration of circular relative to linear granularities (a). Circular granularities can be considered to be cutting the linear granularity into pieces and stacking them (b). The circular granularity creates repeated integer sequences.

In general, any circular granularity relating two linear granularity can be expressed as $C_{(G, H)}(z) = \lfloor z/P(B,G) \rfloor\mod P(G,H)$, where linear granularity $H$ is periodic with respect to linear granularity $G$ with regular mapping and $P(G,H)$ is the period of the grouping $(G, H)$. Table \ref{tab:definitions} shows representation of circular granularities $C_i$ relating two linear granularities with period $P_i$ and minutes as the bottom granularity.

\begin{table}[ht]
\begin{center}
\begin{tabular}{lll}
\toprule
circular granularity & expression & period \\
\midrule
minute-of-hour                               &
  $C_1 = z \mod 60$                     &
  $P_1 = \phantom{99}60$ \\
minute-of-day                                &
  $C_j = z \mod 60*24$                  &
  $P_2= `r 60*24`$\\
hour-of-day                                  &
  $C_3 = \lfloor z/60\rfloor\mod 24$    &
  $P_3 = \phantom{99}24$ \\
hour-of-week                                 &
  $C_4 = \lfloor z/60\rfloor\mod 24*7$  &
  $P_4= \phantom{9}`r 24*7`$\\
day-of-week                                  &
  $C_5 = \lfloor z/24*60\rfloor \mod 7$ &
  $P_5= \phantom{999}7$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Examples of circular granularities with bottom granularity minutes. Circular granularity $C_i$ relates two linear granularities one of which groups periodically into the other with regular mapping and period $P_i$. Circular granularities can be expressed using modular arithmetic due to their regular mapping. }
\label{tab:definitions}
\end{table}

@@

A **quasi-circular** granularity can not be defined using modular arithmetic since they are formed using two linear granularities with irregular mapping. However, they are still formed with linear granularities, one of which "groups periodically into" the other. \autoref{tab:quasi} shows some example of quasi-circular granularities ($Q_i$) with ($P_i$) denoting the plausible choices of period of the grouping of two linear granularities.

\begin{table}[ht]
\begin{center}
\begin{tabular}{lr@{~}lr@{~}r}
\toprule
quasi-circular granularity && potential period lengths\\
\midrule
$Q_1 =$ day-of-month && $P_1 = 31, 30, 29, 28$\\
$Q_2 =$ hour-of-month && $P_2 = 24*31, 24*30, 24*29, 24*28$\\
$Q_3 =$ day-of-year && $P_3 = 366, 365$\\
$Q_4 =$ week-of-month && $P_4 = 5, 4$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Examples of quasi-circular granularities $Q_i$ with potential period lengths $P_i$. These quasi-circular granularities relate two linear granularities one of which groups periodically into the other with irregular mapping leading to many potential period lengths and hence can not be expressed through modular arithmetic. }
\label{tab:quasi}
\end{table}

\begin{definition}\label{def:quasicircular}
A {\bf quasi-circular granularity} $Q_{B, G'}$ relates linear granularities $G'$ and bottom granularity $B$, if
\begin{equation}\label{eq:quasi}
\begin{split}
Q_{B, G'}(z) =
z - \sum_{w=0}^{k-1}\vert T_{w \mod R'} \vert, & \quad \text{for}\quad z \in T_{k}
\end{split}
\end{equation}
where,
$z \in \mathbb{Z}_{\geq 0}$ denotes the index set,
$B$ denotes a full-integer labelled bottom granularity which groups periodically into linear granularity $G'$ with irregular mapping, $P'$ and $R'$ are the period of the grouping $(B, G')$ and the number of granules of $G'$ in $P'$, $T_w$ are the sets of indices of $B$ describing $G'(w)$ such that $G'(w) = \bigcup_{z \in T_w}B(z)$ and $\vert T_w \vert$ is the cardinality of set $T_w$.
\end{definition}

Consider $G'$ such that every two consecutive granules of $G'$ are made up of $7$ and $5$ granules of $B$ respectively within each period of the grouping ($B$, $G'$). Then $Q_{B, G'}$ is a repetitive categorization of time, similar to circular granularities, except that the number of granules of $B$ is not necessarily the same across different granules of $G'$. Here, $T_0 = \{0, 1, \dots, 6\}$ and $T_1 = \{7, \dots 11\}$. Hence using Definition \autoref{def:quasicircular} we will have:
$$
  Q_{B,H'}(10)  = 10 - \sum_{w=0}^{1-1}\vert T_{w \mod 2}\vert =3
$$
since $10 \in T_{1}$.

If linear granularity $G'$ is periodical with respect to $B$ with irregular mapping, then there exist $R'$, $P' \in \mathbb{Z}_+$ such that if $G'(w) = \bigcup_{z \in T_w}B(z)$ then $$G'(w) = \bigcup_{z \in T_w \mod R'}B(P'*\lfloor w/R' \rfloor + z)$$ (from Definition \ref{def:periodical}) Here $w \mod R'$ represents the index that must be shifted to obtain $G'(w)$. The idea here is if we know the composition of each of the granules of $G'$ in terms of granules of $B$ for one period, we can find the composition of any granule of $G'$ beyond a period since the "pattern" repeats itself along the time domain due to the periodic property. The periodic property also ensures that $\vert T_w \vert = \vert T_{w\mod R'} \vert$ since every $w^{\text{th}}$ and $(w+R')^{\text{th}}$ granule of $G'$ will have the same number of granules of $B$. The term $\sum_{w=0}^{k-1}\vert T_{w}\vert$ in Definition \autoref{def:quasicircular} denotes the number of granules of $B$ till the $(k-1)^{\text{th}}$ granule of $G'$. Since $\vert T_w \vert = \vert T_{w\mod R'} \vert$, the number of granules of $B$ till the $(k-1)^{\text{th}}$ granule of $G'$ becomes $\sum_{w=0}^{k-1}\vert T_{w \mod R'}\vert$ in Definition \autoref{def:quasicircular}.

@@

\begin{example}
{\rm Consider a school semester which always lasts for 18 weeks and 2 days, starting with one week of orientation followed by an in-session period of 6 weeks, a semester-break of 1 week and again an in-session period of 7 weeks and 1 week study break before final exams which continue for 16 days. Let the linear granularities $M_1$ and $M_2$ denote in-session semester period and semester break periods respectively. Both $M_1$, $M_2$ and $M = M_{1}\bigcup M_{2}$ denoting the semester week type are aperiodic with respect to days ($B$) or weeks ($G$). Hence $A_{B, M}$ denoting day of the semester week type would be an aperiodic cyclic granularity. This is because the placement of the semester within an year would vary across years. \autoref{fig:aperiodic-example} b shows the stack display of time with granules representing same categories (semester break/in-session) stacked on top of one another. \autoref{fig:aperiodic-example} (a) representing the linear display of time is useful in manifesting how the categories would be determined with respect to the bottom granularities using Definition \ref{def:aperiodic}. It is interesting to note here that $Q_{H, M}$ denoting semester week of the semester week type would be a quasi-circular granularity since the distribution of semester weeks within a semester is assumed to remain constant over years.}
\end{example}

@@

\begin{definition}\label{def:norderup}
The hierarchy table contains {\bf multiple-order-up} granularities which are cyclic granularities that are nested within multiple levels.
A {\bf single-order-up} is a cyclic granularity which is nested within a single level. It is a special case of multiple-order-up granularity.
\end{definition}

\begin{example}
{\rm In \autoref{tab:tab-mayan}, kin-of-tun or kin-of-baktun are examples of multiple-order-up granularities and single-order-up granularities are kin-of-uinal, uinal-of-tun etc.}
\end{example}

@@

Visualizing distributions can be misleading if statistical transformations are performed on rarely occurring categories (Section \ref{sec:summarize-measured}). Even when there are no rarely occurring events, number of observations might vary hugely within or across each facet. This might happen due to missing observations in the data or uneven locations of events in time domain. In such cases, the statistical transformations should be used with caution as sample sizes would directly affect both the variance and consequently the confidence interval of the estimators.

@@

The tsibble object `smart_meter10` from R package `gravitas` [@R-gravitas] consisting of `reading_datetime`, `customer_id` and `general_supply_kwh` denoting the index, key and measured variable of the tsibble is used to facilitate the systematic exploration. While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing to consider is which cyclic time granularities we can look at exhaustively. Let us consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, month, year). Since the interval of this tsibble is 30 minutes, the temporal granularities may range from half-hour to year. Considering $6$ linear granularities half-hour, hour, day, week, month and year in the hierarchy table, $N_C = (6*5/2) = 15$. If $N_C$ seem too large, the smallest and largest linear granularities could be considered to be removed for analysis. Granularities half-year and year are removed to have $N_C = (4*3/2) = 6$ and obtain cyclic granularities namely "hour_day", "hour_week", "hour_month", "day_week", "day_month" and "week_month", read as "hour of the day", etc. Further, we add cyclic granularity day-type( "wknd_wday") to capture weekend and weekday behavior. Now that we have a list of cyclic granularities to look at, we should be able to compute them using Section \ref{sec:cyclic-calendar}.

@@

From the search list, $N_C = 7$ cyclic granularities are chosen for which we would like to derive insights of energy behavior. Recalling the data structure <$C_i$, $C_j$, `general_supply_kwh`> for exploration $\forall i, j \in \{1, 2, \ldots, 7\}$, each of these $7$ cyclic granularities can either be mapped to x-axis or to facet. Choosing $2$ of the possible $7$ granularities, which is equivalent to having $^{7}P_2 = 42$ candidates for visualization. Harmonies can be identified among those $42$ possibilities to narrow the search. \autoref{tab:harmony-tab} shows $16$ harmony pairs after removing clashes and any cyclic granularities with levels more than $31$, as effective exploration becomes difficult with many levels (Section \ref{sec:levels}).

>>>>

 The methods are implemented in the open source R package `gravitas`, providing functions for creating granularities and exploring the associated time series which are consistent with a tidy workflow (@Grolemund2018-po), and the probability distributions can be examined using the range of graphics available in `ggplot2` [@Wickham2009pk].
bibliography: [bibliography.bib]
preamble: >
  \usepackage{mathtools,amssymb,booktabs,amsthm}
  \def\mod{~\text{mod}~}
  \newtheorem{definition}{Definition}
  \usepackage{mathptmx}
  \usepackage{caption}
  \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
  \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
  \captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
output:
  bookdown::pdf_book:
    base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
    keep_tex: yes
---

@@

Cyclic granularities represent cyclical repetitions in time. They can be thought of as additional categorizations of time that are not linear. Cyclic granularities can be constructed from two linear granularities, that relate periodically; the resulting cycles can be either _regular_ (**circular**), or _irregular_ (**quasi-circular**).

@@

\begin{definition}\label{def:circular}
A \textbf{circular granularity} $C_{B, G}$ relates linear granularity $G$ to bottom granularity $B$, if
\begin{equation} \label{eq:circular-gran}
\begin{split}
C_{B, G}(z) & = z\mod P(B, G) \quad \forall z \in \mathbb{Z}_{\geq 0} \\
\end{split}
\end{equation}
where
$z$ denotes the index set,
$B$ groups periodically into $G$ with regular mapping and period $P(B, G)$.
\end{definition}

@@

(ref:circular-dow) a. Index sets for some linear and circular granularities.  b. Circular granularities can be constructed by slicing the linear granularity into pieces and stacking them.

\autoref{fig:circular-dow} illustrates some linear and cyclical granularities. Cyclical granularities are constructed be cutting the linear granularity into pieces, and stacking them to match the cycles (as shown in b). $B, G, H$ (day, week, fortnight, respectively) are linear granularities. The circular granularity $C_{B, G}$ (day-of-week) is constructed from $B$ and $G$, while  circular granularity $C_{B, H}$ (day-of-fortnight) is constructed from $B$ and $H$. These overlapping cyclical granularities share elements from the linear granularity. Each of $C_{B , G}$ and $C_{B , H}$ consist of repeated patterns $\{0, 1, \dots, 6\}$ and $\{0, 1, \dots, 13\}$ with $P=7$ and $P=14$ respectively.

Suppose ${L}$ is a label mapping that defines a unique label for each index $\ell \in \{ 0,1,\dots, (P-1)\}$. For example, the label mapping $L$ for $C_{B, G}$ can be defined as
$$
  L: \{0,1, \dots, 6\} \longmapsto\ \{\text{Sunday}, \text{Monday}, \dots, \text{Saturday}\}.
$$

In general, any circular granularity relating two linear granularities can be expressed as
$$
  C_{(G, H)}(z) = \lfloor z/P(B,G) \rfloor\mod P(G,H),
$$
where $H$ is periodic with respect to $G$ with regular mapping and period $P(G,H)$. Table&nbsp;\ref{tab:definitions} shows several circular granularities constructed using minutes as the bottom granularity.

\begin{table}[ht]
\begin{center}
\begin{tabular}{lll}
\toprule
Circular granularity & Expression & Period \\
\midrule
minute-of-hour                               &
  $C_1 = z \mod 60$                     &
  $P_1 = \phantom{99}60$ \\
minute-of-day                                &
  $C_j = z \mod 60*24$                  &
  $P_2= `r 60*24`$\\
hour-of-day                                  &
  $C_3 = \lfloor z/60\rfloor\mod 24$    &
  $P_3 = \phantom{99}24$ \\
hour-of-week                                 &
  $C_4 = \lfloor z/60\rfloor\mod 24*7$  &
  $P_4= \phantom{9}`r 24*7`$\\
day-of-week                                  &
  $C_5 = \lfloor z/24*60\rfloor \mod 7$ &
  $P_5= \phantom{999}7$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Examples of circular granularities with bottom granularity minutes. Circular granularity $C_i$ relates two linear granularities one of which groups periodically into the other with regular mapping and period $P_i$. Circular granularities can be expressed using modular arithmetic due to their regular mapping. }
\label{tab:definitions}
\end{table}

@@

A **quasi-circular** granularity cannot be defined using modular arithmetic  because of the irregular mapping. However, they are still formed with linear granularities, one of which groups periodically into the other. \autoref{tab:quasi} shows some examples of quasi-circular granularities.

\begin{table}[ht]
\centering
\begin{tabular}{lr@{~}lr@{~}r}
\toprule
Quasi-circular granularity && Possible period lengths\\
\midrule
$Q_1 =$ day-of-month && $P_1 = 31, 30, 29, 28$\\
$Q_2 =$ hour-of-month && $P_2 = 24\times 31, 24\times 30, 24\times 29, 24\times 28$\\
$Q_3 =$ day-of-year && $P_3 = 366, 365$\\
$Q_4 =$ week-of-month && $P_4 = 5, 4$\\
\bottomrule
\end{tabular}
\caption{Examples of quasi-circular granularities relating two linear granularities with irregular mapping leading to several possible period lengths.}
\label{tab:quasi}
\end{table}

\begin{definition}\label{def:quasicircular}
A \textbf{quasi-circular granularity} $Q_{B, G'}$ relates linear granularity $G'$ and bottom granularity $B$ if
\begin{equation}\label{eq:quasi}
Q_{B, G'}(z) =
z - \sum_{w=0}^{k-1}\vert T_{w \mod R'} \vert, \quad \text{for}\quad z \in T_{k},
\end{equation}
where
$z$ denotes the index set,
$B$ groups periodically into $G'$ with irregular mapping,
$P'$ and $R'$ are the period of the grouping $(B, G')$ and the number of granules of $G'$ in $P'$,
$T_w$ are the sets of indices of $B$ describing $G'(w)$ such that $G'(w) = \bigcup_{z \in T_w}B(z)$,
and $\vert T_w \vert$ is the cardinality of set $T_w$.
\end{definition}

For example, suppose consecutive granules of $G'$ are alternately made up of $7$ and $5$ granules of $B$ within each period of the grouping ($B$, $G'$). Then $Q_{B, G'}$ is a repetitive categorization of time, similar to circular granularities, except that the number of granules of $B$ is not the same across different granules of $G'$. Here, $T_0 = \{0, 1, \dots, 6\}$ and $T_1 = \{7, \dots 11\}$. Hence using Definition \autoref{def:quasicircular} we will have:
$$
  Q_{B,H'}(10)  = 10 - \sum_{w=0}^{1-1}\vert T_{w \mod 2}\vert =3
$$
since $10 \in T_{1}$.

If linear granularity $G'$ is periodical with respect to $B$ with irregular mapping, then there exist $R'$, $P' \in \mathbb{Z}_+$ such that if $G'(w) = \bigcup_{z \in T_w}B(z)$ then $$G'(w) = \bigcup_{z \in T_w \mod R'} B(P'*\lfloor w/R' \rfloor + z)$$ (from Definition \ref{def:periodical}). Here $w \mod R'$ represents the index that must be shifted to obtain $G'(w)$. The idea here is if we know the composition of each of the granules of $G'$ in terms of granules of $B$ for one period, we can find the composition of any granule of $G'$ beyond a period since the "pattern" repeats itself along the time domain due to the periodic property. The periodic property also ensures that $\vert T_w \vert = \vert T_{w\mod R'} \vert$ since every $w^{\text{th}}$ and $(w+R')^{\text{th}}$ granule of $G'$ will have the same number of granules of $B$. The term $\sum_{w=0}^{k-1}\vert T_{w}\vert$ in Definition \autoref{def:quasicircular} denotes the number of granules of $B$ till the $(k-1)^{\text{th}}$ granule of $G'$. Since $\vert T_w \vert = \vert T_{w\mod R'} \vert$, the number of granules of $B$ till the $(k-1)^{\text{th}}$ granule of $G'$ becomes $\sum_{w=0}^{k-1}\vert T_{w \mod R'}\vert$ in Definition \autoref{def:quasicircular}.

@@

Consider a school semester which always lasts for 18 weeks and 2 days, starting with one week of orientation followed by an in-session period of 6 weeks, a semester-break of 1 week and again an in-session period of 7 weeks and 1 week study break before final exams which continue for 16 days. Let the linear granularities $M_1$ and $M_2$ denote in-session semester period and semester break periods respectively. Both $M_1$, $M_2$ and $M = M_{1}\bigcup M_{2}$ denoting the semester week type are aperiodic with respect to days ($B$) or weeks ($G$). Hence $A_{B, M}$ denoting day of the semester week type would be an aperiodic cyclic granularity. This is because the placement of the semester within an year would vary across years. \autoref{fig:aperiodic-example} b shows the stack display of time with granules representing same categories (semester break/in-session) stacked on top of one another. \autoref{fig:aperiodic-example} (a) representing the linear display of time is useful in manifesting how the categories would be determined with respect to the bottom granularities using Definition \ref{def:aperiodic}. It is interesting to note here that $Q_{H, M}$ denoting semester week of the semester week type would be a quasi-circular granularity since the distribution of semester weeks within a semester is assumed to remain constant over years.

@@

\begin{definition}\label{def:norderup}
The hierarchy table contains \textbf{multiple-order-up} granularities which are cyclic granularities that are nested within multiple levels.
A \textbf{single-order-up} is a cyclic granularity which is nested within a single level. It is a special case of multiple-order-up granularity.
\end{definition}

In the Mayan calendar (Table \@ref(tab:tab-mayan)), kin-of-tun or kin-of-baktun are examples of multiple-order-up granularities and single-order-up granularities are kin-of-uinal, uinal-of-tun etc.

@@

Visualizing distributions can be misleading if statistical transformations are performed on rarely occurring categories (Section&nbsp;\ref{sec:summarize-measured}). Even when there are no rarely occurring events, number of observations might vary hugely within or across each facet. This might happen due to missing observations in the data or uneven locations of events in time domain. In such cases, the statistical transformations should be used with caution as sample sizes would directly affect both the variance and consequently the confidence interval of the estimators.

@@

The tsibble object `smart_meter10` from R package `gravitas` [@R-gravitas] consisting of `reading_datetime`, `customer_id` and `general_supply_kwh` denoting the index, key and measured variable of the tsibble is used to facilitate the systematic exploration. While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing to consider is which cyclic time granularities we can look at exhaustively. Let us consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, month, year). Since the interval of this tsibble is 30 minutes, the temporal granularities may range from half-hour to year. Considering $6$ linear granularities half-hour, hour, day, week, month and year in the hierarchy table, $N_C = (6*5/2) = 15$. If $N_C$ seem too large, the smallest and largest linear granularities could be considered to be removed for analysis. Granularities half-year and year are removed to have $N_C = (4*3/2) = 6$ and obtain cyclic granularities namely "hour_day", "hour_week", "hour_month", "day_week", "day_month" and "week_month", read as "hour of the day", etc. Further, we add cyclic granularity day-type( "wknd_wday") to capture weekend and weekday behavior. Now that we have a list of cyclic granularities to look at, we should be able to compute them using Section&nbsp;\ref{sec:cyclic-calendar}.

@@

From the search list, $N_C = 7$ cyclic granularities are chosen for which we would like to derive insights of energy behavior. Recalling the data structure <$C_i$, $C_j$, `general_supply_kwh`> for exploration $\forall i, j \in \{1, 2, \ldots, 7\}$, each of these $7$ cyclic granularities can either be mapped to x-axis or to facet. Choosing $2$ of the possible $7$ granularities, which is equivalent to having $^{7}P_2 = 42$ candidates for visualization. Harmonies can be identified among those $42$ possibilities to narrow the search. \autoref{tab:harmony-tab} shows $16$ harmony pairs after removing clashes and any cyclic granularities with levels more than $31$, as effective exploration becomes difficult with many levels (Section&nbsp;\ref{sec:levels}).
